Exploring mathematical objects from custom-tailored mathematical universes

### 2020-02-20 paper-filmat.tex
With proper title

%\title[]{Exploring mathematical objects from custom-tailored mathematical universes}
%\author{Ingo Blechschmidt}
%\address{Universität Augsburg \\
%Institut für Mathematik \\
%Universitätsstr. 14 \\
%86159 Augsburg, Germany}
%\email{ingo.blechschmidt@math.uni-augsburg.de}

@@

%\maketitle
\thispagestyle{empty}

\begin{center}
  \begin{tikzpicture}
    \node (comment) at (0,0) {
      \begin{minipage}{0.6\textwidth}
      \emph{To the anonymous referees:}
      \bigskip

      Thank you for your volunteer work. It is very much appreciated. I am looking
      forward to your comments.
      \bigskip

      \hfill -- the anonymous author
      \end{minipage}
    };

    \node[draw=mypurple, very thick, rectangle, rounded corners, inner sep=5pt] [fit = (comment)] (foo) {};
  \end{tikzpicture}
\end{center}
\bigskip

>>>>

\title[]{Exploring mathematical objects from custom-tailored mathematical universes}
\author{Ingo Blechschmidt}
\address{Universität Augsburg \\
Institut für Mathematik \\
Universitätsstr. 14 \\
86159 Augsburg, Germany}
\email{ingo.blechschmidt@math.uni-augsburg.de}

@@

\maketitle
\thispagestyle{empty}
